D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
Add disclaimer about rfe "ordering"
The rfe relation doesn't _cause_ ordering of hardware instructions; it's
more like a _result_ of the order.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Listing 10: s/atomic<volatile int>/volatile atomic<int>
Make it match the similar use cases in the standard.

Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Dependencies aren't the only mechanism that can lead to
ordering in hardware executions.
The simplest alternative is a load reading from a store in another
thread, i.e., the rfe relation.
As mentioned in Section~\ref{sec:Simple OOTA Cycle} above, a CPU does
not make the value of a store instruction available for other CPUs to
load until the store commits or some time later.
And after this happens, it takes some time for the information about
the store to travel from that CPU to others, owing to the inescapable
facts that processors have nonzero size and information cannot travel
faster than the speed of light.
Since the load instruction cannot commit until its output (the value it
reads) is fully determined, it must commit after the store it reads
from.

@@

\begin{listing}
\begin{verbatim}
 1 atomic<volatile int> x, y;
 2
 3 void thread1() {
 4   int r1 = x.load(memory_order_relaxed);
 5   y.store(r1, memory_order_relaxed);
 6 }
\end{verbatim}
\caption{Volatile Accesses and Dependencies}
\label{lst:Volatile Accesses and Dependencies}
\end{listing}

>>>>

Dependencies aren't the only mechanism that can lead to
ordering in hardware executions.
The simplest alternative is a load reading from a store in another
thread, i.e., the rfe relation.
As mentioned in Section~\ref{sec:Simple OOTA Cycle} above, a CPU does
not make the value of a store instruction available for other CPUs to
load until the store commits or some time later.
And after this happens, it takes some time for the information about
the store to travel from that CPU to others, owing to the inescapable
facts that processors have nonzero size and information cannot travel
faster than the speed of light.
Since the load instruction cannot commit until its output (the value it
reads) is fully determined, it must commit after the store it reads
from.
(To be fair, this should be considered more as a \emph{result} of
ordering rather than a \emph{cause} of ordering, in that
if a load commits before a store on another thread then it
cannot possibly read from that store.)

@@

\begin{listing}
\begin{verbatim}
 1 volatile atomic<int> x, y;
 2
 3 void thread1() {
 4   int r1 = x.load(memory_order_relaxed);
 5   y.store(r1, memory_order_relaxed);
 6 }
\end{verbatim}
\caption{Volatile Accesses and Dependencies}
\label{lst:Volatile Accesses and Dependencies}
\end{listing}
